---
title: "Prop1 IFCB"
author: "Megan Hepner"
date: "2/27/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r library, include=FALSE}

library(plotly)
#devtools::install_github("rstudio/leaflet#346")
library(leaflet)
library(crosstalk)
library(htmltools)
library(rjson)
library(jsonlite)
library(RCurl)
library(rgdal)
library(sf)
library(tidyverse)
library(dplyr)
library(rnaturalearth) 
library(ggplot2)
library(ggspatial)
devtools::install_github("rstudio/rsconnect")

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning=FALSE)

```

```{r read in data, echo=FALSE}

Prop2 = read_csv("/Volumes/GoogleDrive/My Drive/SCCOOS/Admin_SCCOOS/FY19/Extramural Proposals/OPC-Prop1-Round3/Figures/Program_Locations.csv") #User/mhepner

Prop2 = Prop2 %>% #221x3, 10 groups 
  select(Program, Type2, Station_Locations, Latitude, Longitude) %>%
  group_by(Type2)
         
```

## IFCB Proposed Sampling Locations

###Ship-Based Sampling
| CalCOFI (113 stations) – run offline with Scripps Pier IFCB
| OCSD SCBRWQP (84 stations) – run offline with Newport Pier IFCB 
| Plumes and Blooms (7 stations) – run offline with **new IFCB #8**
| SBC-LTER (4 stations) – run offline with **new IFCB #8**
| Trinidad Head Line (4 stations) – run offline with Trinidad Pier IFCB 

###Shore-Based Sampling (real-time)
| CeNCOOS Shore Station (2 stations)
|     1. Trinidad Pier – **new IFCB #1** (shared with THL)
|     2. Bodega Bay – **new IFCB #5**
| HABMAP/SCCOOS Shore Stations (4 stations)
|     1. Santa Cruz Wharf – *current IFCB* 
|     2. Stearns Wharf – **new IFCB #2**
|     3. Newport Pier – **new IFCB #3** (shared with OCSD SCBRWQP)
|     4. Scripps Pier – **new IFCB #4** (shared with CalCOFI)

###Moorings (real-time)
| Catalina Sea Ranch NOMAD Buoy – *current IFCB* 
| Del Mar Mooring – **new IFCB #6**
| MBARI M1 Mooring – **new IFCB #7**

###Interactive Map 
```{r leaflet Program, echo=FALSE}

Prop1.df = as.data.frame(Prop2)
l <- leaflet() %>%
  addProviderTiles(providers$Esri.OceanBasemap)

pal <- colorFactor(c("navy", "red", "green"),
                   domain = unique(Prop1.df$Program))

test4 = leaflet() %>% 
      addProviderTiles(providers$Esri.OceanBasemap) %>%
      addCircleMarkers(data=Prop1.df, 
                       color=~pal(Program),
                       stroke= FALSE, fillOpacity = 0.5,
                       lng=~Longitude, 
                       lat=~Latitude,
                       label=paste(
                         Prop1.df$Program, ",",
                         Prop1.df$Type2, "," ,
                         Prop1.df$Station_Locations)) 
test4

```

```{r Program, include=FALSE, echo=FALSE}

states <- ne_states(
  country = c("Canada",
              "United States of America",
              "Mexico"),
  returnclass = 'sf') %>% 
  filter(name %in% c("California","Oregon",
                     "Washington","Nevada",
                     "British Columbia",
                     "Baja California",
                     "Baja California Sur"))

## test2
wc.lat  <- range(Prop2$Latitude, na.rm=T) #29.84637 41.06110
wc.long <- range(Prop2$Longitude, na.rm=T) #-126.4856 -117.1008

#Create base map
test2 = base.map <- ggplot() +
  geom_sf(data=states)+
  geom_point(data = Prop2,
             aes(Longitude, Latitude,  
                 color=Program), #shape=Program # The shape palette can deal with a maximum of 6 discrete values
             size=2.5) + 
  xlab("Longitude") +
  ylab("Latitude") + 
  #ggtitle("Sampling Locations by Program")+
  annotation_scale(location = "bl", 
                   width_hint = 0.5) +
  coord_sf(xlim = wc.long,
           ylim = wc.lat) +
  theme_bw()
test2

ggsave(plot=test2, file="/Volumes/GoogleDrive/My Drive/SCCOOS/Admin_SCCOOS/FY19/Extramural Proposals/OPC-Prop1-Round3/Program_Map.png")
```

```{r leaflet Platform, include=FALSE, echo=FALSE, }

#include=FALSE

pal2 <- colorFactor(c("red", "green", "navy"),
                   domain = unique(Prop1.df$Type2))

test5 = leaflet() %>% 
      addProviderTiles(providers$Esri.OceanBasemap) %>%
      addCircleMarkers(data=Prop1.df, 
                       color=~pal2(Type2),
                       popup=paste(
                         "Program:", Prop1.df$Program, "<br>",
                         "Platform:", Prop1.df$Type2, "<br>"),
                       stroke= FALSE, fillOpacity = 0.5,
                       lng=~Longitude, 
                       lat=~Latitude,
                       label=paste(
                         Prop1.df$Program, ",",
                         Prop1.df$Type2, "," ,
                         Prop1.df$Station_Locations)) 
                         
test5

```

```{r Platform, include=FALSE, echo=FALSE}

states <- ne_states(
  country = c("Canada",
              "United States of America",
              "Mexico"),
  returnclass = 'sf') %>% 
  filter(name %in% c("California","Oregon",
                     "Washington","Nevada",
                     "British Columbia",
                     "Baja California",
                     "Baja California Sur"))

wc.lat  <- range(Prop2$Latitude, na.rm=T) #29.84637 41.06110
wc.long <- range(Prop2$Longitude, na.rm=T) #-126.4856 -117.1008

#Create base map
test3 = base.map <- ggplot() +
  geom_sf(data=states)+
  geom_point(data = Prop2,
             aes(Longitude, Latitude,  
                 color=Type2), #shape=Program # The shape palette can deal with a maximum of 6 discrete values
             size=2.5) + 
  xlab("Longitude") +
  ylab("Latitude") + 
  #ggtitle("Sampling Locations by Platform Type")+
  labs(color="Platform Type")+
  annotation_scale(location = "bl", 
                   width_hint = 0.5) +
  coord_sf(xlim = wc.long,
           ylim = wc.lat) +
  theme_bw()
test3

ggsave(plot=test3, file="/Volumes/GoogleDrive/My Drive/SCCOOS/Admin_SCCOOS/FY19/Extramural Proposals/OPC-Prop1-Round3/figures/Platform_Map.png")
```

```{r Platform and Program , include=FALSE, echo=FALSE}

Prop1 = read_csv("/Volumes/GoogleDrive/My Drive/SCCOOS/Admin_SCCOOS/FY19/Extramural Proposals/OPC-Prop1-Round3/Figures/Program_Locations.csv") #User/mhepner

MPA_shape = read_sf("/Volumes/GoogleDrive/My Drive/SCCOOS/CDPH/ArcGIS/shapes/CA_MPA_shapefiles/ds582.shp", layer="SHAPEFILE") #ds582_CaliforniaMarineProtectedAreas.lyr

Prop1 = Prop1 %>% #221x3, 10 groups 
  select(Program, Type2, Station_Locations, Latitude, Longitude) %>%
  group_by(Type2)

states <- ne_states(
  country = c("Canada",
              "United States of America",
              "Mexico"),
  returnclass = 'sf') %>% 
  filter(name %in% c("California","Oregon",
                     "Washington","Nevada",
                     "British Columbia",
                     "Baja California",
                     "Baja California Sur"))

## test2
wc.lat  <- range(Prop1$Latitude, na.rm=T) #29.84637 41.06110
wc.long <- range(Prop1$Longitude, na.rm=T) #-126.4856 -117.1008

#Create base map
test1 = base.map <- ggplot() +
  geom_sf(data=states)+
  geom_point(data = Prop1,
             aes(Longitude, Latitude,  
                 color=Type2, shape=Program), #shape=Program # The shape palette can deal with a maximum of 6 discrete values
             size=2.5) + 
  xlab("Longitude") +
  ylab("Latitude") + 
  #ggtitle("Sampling Locations by Program")+
  annotation_scale(location = "bl", 
                   width_hint = 0.5) +
  coord_sf(xlim = wc.long,
           ylim = wc.lat) +
  theme_bw()
test1

ggsave(plot=test1, file="/Volumes/GoogleDrive/My Drive/SCCOOS/Admin_SCCOOS/FY19/Extramural Proposals/OPC-Prop1-Round3/Figures/Program_Map.png", width=8, height = 8)
```

```{r IFCB updated sites}

library(plotly)
#devtools::install_github("rstudio/leaflet#346")
library(leaflet)
library(crosstalk)
library(htmltools)
library(rjson)
library(jsonlite)
library(RCurl)
library(rgdal)
library(sf)
library(tidyverse)
library(dplyr)
library(rnaturalearth) 
library(ggplot2)
library(ggspatial)
devtools::install_github("rstudio/rsconnect")

#knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning=FALSE)

IFCB_lat_long = read_csv("/Volumes/GoogleDrive/My Drive/SCCOOS/Admin_SCCOOS/FY19/Extramural Proposals/OPC-Prop1-Round3/Resubmission/IFCB_Sites.csv")

#STATIC MAP 
states <- ne_states(
  country = c("Canada",
              "United States of America",
              "Mexico"),
  returnclass = 'sf') %>% 
  filter(name %in% c("California","Oregon",
                     "Washington","Nevada",
                     "British Columbia",
                     "Baja California",
                     "Baja California Sur"))

## test2
#wc.lat  <- range(HABMAP_lat_long$Latitude, na.rm=T) #29.84637 41.06110
#wc.long <- range(HABMAP_lat_long$Longitude, na.rm=T) #-126.4856 -117.1008

#Create base map 
test1 = base.map <- ggplot() +
  geom_sf(data=states)+
  geom_point(data = IFCB_lat_long,
             aes(Longitude, Latitude,  
                 color=Funded), #shape=Program # The shape palette can deal with a maximum of 6 discrete values
             size=4) + 
  xlab("Longitude") +
  ylab("Latitude") + 
  #ggtitle("Sampling Locations by Program")+
  annotation_scale(location = "bl", 
                   width_hint = 0.5) +
  coord_sf(xlim = wc.long,
           ylim = wc.lat) +
  theme_bw()
test1

ggsave(plot=test1, file="/Volumes/GoogleDrive/My Drive/SCCOOS/Admin_SCCOOS/FY19/Extramural Proposals/OPC-Prop1-Round3/Resubmission/IFCB_Sites.png", width=8, height = 8)

HABMAP.df = as.data.frame(IFCB_lat_long)
l <- leaflet() %>%
  addProviderTiles(providers$Esri.OceanBasemap)

pal <- colorFactor(c("navy", "green"),
                   domain = unique(IFCB_lat_long$Funded))

test4 = leaflet() %>% 
      addProviderTiles(providers$Esri.OceanBasemap) %>%
      addCircleMarkers(data=IFCB_lat_long, 
                       color=~pal(Funded),
                       stroke= FALSE, fillOpacity = 0.5,
                       lng=~Longitude, 
                       lat=~Latitude,
                       label=paste(
                         IFCB_lat_long$Sites, ",",
                         IFCB_lat_long$Funded, ",")) 
test4

library(ggmap)
library(maps)
library(mapdata)

states <- map_data("state")
dim(states)
ca_df <- subset(states, region == "california")

counties <- map_data("county")
ca_county <- subset(counties, region == "california")

ca_base <- ggplot(data = ca_df, mapping = aes(x = long, y = lat, group = group)) + 
  coord_fixed(1.3) + 
  geom_polygon(color = "black", fill = "gray")
ca_base + theme_nothing()


#add counties 
ca_base + theme_nothing() + 
  geom_polygon(data = ca_county, fill = NA, color = "white") +
  geom_polygon(color = "black", fill = NA)  # get the state border back on top

test3 = ca_base + theme_nothing() + 
  geom_polygon(data = ca_county, aes(x = long, y = lat), fill = NA, color = "grey82") +
  geom_polygon(color = "black", fill = NA)+  # get the state border back on top
  #annotation_scale(location = "bl", 
   #                width_hint = 0.5) +
  geom_point(data = IFCB_lat_long,
             aes(Longitude, Latitude,  
                 color=Funded, group=Shape), #shape=Program # The shape palette can deal with a maximum of 6 discrete values
             size=4) +
  geom_text(data = IFCB_lat_long, aes(x=Longitude, y=Latitude, label=Sites, group=Funded), hjust=0, nudge_x = 0.3)
  #coord_quickmap()

ggsave(plot=test3, file="/Volumes/GoogleDrive/My Drive/SCCOOS/Admin_SCCOOS/FY19/Extramural Proposals/OPC-Prop1-Round3/Resubmission/IFCB_Sites_V2.png", width=8, height = 8)

```