---
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(dygraphs) #dygraphs 
library(ggplot2) #ggplot
library(tidyverse)
library(dplyr)
library(htmlwidgets)
library(xts)

TMMC_data = read.csv('/Volumes/GoogleDrive/My Drive/SCCOOS/CA_HAB_Bulletin/Stranding_Data/Data/1998-2019_TMMC_DA.csv')

# dygraph_test = TMMC_data %>%
#   select(Age_Class, Sex, Common_Name, Strand_Date, Stranding_City, Stranding_County,Stranding_Locality,Latitude, Longitude) %>%
#   na.omit() %>%
#   mutate(Strand_Date = as.Date(Strand_Date, format ="%m/%d/%Y")) %>%
#   mutate(Year = format(as.Date(Strand_Date, format="%m/%d/%Y"), "%Y")) %>% 
#   mutate(Year_Month = format(as.Date(Strand_Date), "%Y-%m")) %>% 
#   group_by(Year_Month) %>% #Age_Class, 
#   summarize(Counts = length(Year_Month))
# 
# dygraph_test$Year_Month = as.yearmon(dygraph_test$Year_Month, "%Y-%m")
# don2 = xts(x=dygraph_test$Counts, order.by = dygraph_test$Year_Month)
# 
# dygraph(don2, main = "TMMC California Sea Lion Strandings Suspected DA", xlab = "", ylab= "Sea Lion Strandings") %>%
#   dyOptions(labelsUTC = TRUE, fillGraph=TRUE, fillAlpha=0.4, drawGrid = T, drawPoints = T) %>% #colors="#D8AE5A"
#   dyRangeSelector() %>%
#   dyAxis("x", valueRange = c(1998, 2019))

test2 = TMMC_data %>%
  select(Strand_Date,Common_Name,Stranding_County) %>%
  mutate(Year_Month = format(as.Date(Strand_Date),"%Y-%m")) %>%
  group_by(Year_Month)%>%
  summarize(Strandings=length(Year_Month))

test2$Year_Month = as.yearmon(test2$Year_Month, "%Y-%m")
don3 = xts(x=test2$Strandings, order.by = test2$Year_Month)
```

```{r Dygraph, echo=FALSE}
dygraph(data=don3, main = "TMMC California Sea Lion Strandings Suspected DA", xlab = "", ylab= "Sea Lion Strandings Due to Suspected DA") %>%
  dyOptions(labelsUTC = TRUE, fillGraph=TRUE, fillAlpha=0.4, drawGrid = T, drawPoints = T) %>% #colors="#D8AE5A"
  dyRangeSelector() %>%
  dyAxis("x", valueRange = c(1998, 2019))
```

```{r Dygraph Dataset}

TMMC_data = read.csv('/Volumes/GoogleDrive/My Drive/SCCOOS/CA_HAB_Bulletin/Stranding_Data/Data/1998-2019_TMMC_DA.csv') #2091x22

write_rds(TMMC_data, 'TMMC Dygraph/TMMC_Data.rds')

TMMC_data = TMMC_data %>%
  select(Common_Name,Strand_Date, Stranding_County, Stranding_City, Age_Class) %>%
  filter(Common_Name =='California Sea Lion') %>%
  mutate(Year_Month = format(as.Date(Strand_Date),"%Y-%m")) 

All_Strandings = TMMC_data %>% #224x3
  group_by(Year_Month, Common_Name)%>%
  summarize(Strandings=length(Year_Month))

Group_County = TMMC_data %>% #664x3
  group_by(Year_Month, Stranding_County)%>%
  summarize(County=length(Year_Month))

Group_City = TMMC_data %>% #1177x3 
  group_by(Year_Month, Stranding_City)%>%
  summarize(City=length(Year_Month))

Group_Age = TMMC_data %>% #533x3
  group_by(Year_Month, Age_Class)%>%
  summarize(Age=length(Year_Month))

Bind = left_join(All_Strandings, Group_County, by="Year_Month")