---
title: "HABMAP Data"
author: "Megan Hepner"
date: "6/17/2019"
output: html_document
---

```{r Libraries, echo=T, warning=F, error=F, message=F, tidy=T}

#rm(list=ls()) 
library(rerddap)
library(tidyverse)
library(readr)

select = dplyr::select #override MASS::select 
group_by =  dplyr::group_by #override plotly::group_by
summarise = dplyr::summarise #override plotly::summarise

```

Example [R code](https://rmendels.github.io/Using_rerddap.nb.html) on how to download data from ERDDAP Servers by Roy Mendelssohn and Scott Chamberlain. 

### ERDDAP Dataset ID:
1. [HABs-CalPoly](http://erddap.sccoos.org/erddap/tabledap/HABs-CalPoly.html)
2. [HABs-MontereyWharf](http://erddap.sccoos.org/erddap/tabledap/HABs-MontereyWharf.html)
3. [HABs-NewportPier](http://erddap.sccoos.org/erddap/tabledap/HABs-NewportPier.html) 
4. [HABs-SantaCruzWharf](http://erddap.sccoos.org/erddap/tabledap/HABs-SantaCruzWharf.html) 
5. [HABs-SantaMonicaPier](http://erddap.sccoos.org/erddap/tabledap/HABs-SantaMonicaPier.html)
6. [HABs-ScrippsPier](http://erddap.sccoos.org/erddap/tabledap/HABs-ScrippsPier.html) 
7. [HABs-StearnsWharf](http://erddap.sccoos.org/erddap/tabledap/HABs-StearnsWharf.html)

### HABMAP Variables: 
1. Akashiwo_sanguinea                        
2. Alexandrium_spp                             
3. Ammonium     
4. Avg_Chloro     
5. Avg_Phaeo     
6. Ceratium                      
7. Chl_Volume_Filtered     
8. Chl1   
9. Chl2   
10. Cochlodinium                          
11. DA_Volume_Filtered    
12. dDA                          
13. depth    
14. Dinophysis_spp    
15. Gymnodinium_spp       
16. latitude     
17. Lingulodinium_polyedra                     
18. Location_Code                           
19. longitude    
20. Nitrate   
21. Nitrite     
22. Nitrite_Nitrate   
23. Other_Diatoms                         
24. Other_Dinoflagellates                           
25. pDA                            
26. Phaeo1     
27. Phaeo2    
28. Phosphate    
29. Prorocentrum_spp                              
30. Pseudo_nitzschia_delicatissima_group                              
31. Pseudo_nitzschia_seriata_group                              
32. SampleID                               
33. Silicate     
34. tDA                           
35. Temp                          
36. time    
37. Total_Phytoplankton                           
38. Volume_Settled_for_Counting     

### Pull HABMAP Data from [ERDDAP](http://erddap.sccoos.org/erddap/) 

```{r Download HABMAP Data from ERDDAP, echo=T, tidy=T}

variables = c('Location_Code','time','Alexandrium_spp', 'Akashiwo_sanguinea',"Cochlodinium", "Ceratium", 'Dinophysis_spp', 'Gymnodinium_spp', 'Lingulodinium_polyedra', 'Prorocentrum_spp','Pseudo_nitzschia_delicatissima_group','Pseudo_nitzschia_seriata_group','pDA',  'Ammonium','Avg_Chloro','Avg_Phaeo','Nitrate','Phosphate', 'Silicate', 'Temp')

CalPoly = rerddap::info(datasetid = "HABs-CalPoly", url="http://erddap.sccoos.org/erddap/")
CalPoly_Data = tabledap(CalPoly, fields = variables, 'time>=2008-01-01T00:00:00Z', 'time<=2050-04-17T05:35:00Z', url = "http://erddap.sccoos.org/erddap/")

Monterey = info("HABs-MontereyWharf",url= "http://erddap.sccoos.org/erddap/") 
Monterey_Data = tabledap(Monterey, fields = variables, 'time>=2008-08-01T00:00:00Z', 'time<=2050-04-17T05:35:00Z', url = "http://erddap.sccoos.org/erddap/")

Newport = info("HABs-NewportPier",url= "http://erddap.sccoos.org/erddap/") 
Newport_Data = tabledap(Newport, fields = variables, 'time>=2008-01-01T00:00:00Z', 'time<=2050-04-17T05:35:00Z', url = "http://erddap.sccoos.org/erddap/")

SantaCruz = info("HABs-SantaCruzWharf",url= "http://erddap.sccoos.org/erddap/") 
SantaCruz_Data = tabledap(SantaCruz, fields = variables, 'time>=2008-01-01T00:00:00Z', 'time<=2050-04-17T05:35:00Z', url = "http://erddap.sccoos.org/erddap/")

SantaMonica = info("HABs-SantaMonicaPier",url= "http://erddap.sccoos.org/erddap/")
SantaMonica_Data = tabledap(SantaMonica, fields = variables, 'time>=2008-01-01T00:00:00Z', 'time<=2050-04-17T05:35:00Z', url = "http://erddap.sccoos.org/erddap/")

Scripps = info("HABs-ScrippsPier",url= "http://erddap.sccoos.org/erddap/") 
Scripps_Data = tabledap(Scripps, fields = variables, 'time>=2008-01-01T00:00:00Z', 'time<=2050-04-17T05:35:00Z', url = "http://erddap.sccoos.org/erddap/")

Stearns = info("HABs-StearnsWharf",url= "http://erddap.sccoos.org/erddap/") 
Stearns_Data = tabledap(Stearns, fields = variables, 'time>=2008-01-01T00:00:00Z', 'time<=2050-04-17T05:35:00Z', url = "http://erddap.sccoos.org/erddap/")

#Bind all the Data into one datatable 

HABMAP_Data = dplyr::bind_rows(list(CalPoly_Data, Monterey_Data,Newport_Data,SantaCruz_Data,SantaMonica_Data,Stearns_Data, Scripps_Data)) 

#glimpse(HABMAP_Data)

```

### Arrange Data in Long Format and Save 
```{r HABMAP Data in Long Format}

HABMAP_Data_Long = HABMAP_Data %>%   
  gather(key = "Observations", value = "Measurement", 'Akashiwo_sanguinea', 'Alexandrium_spp','Ceratium', 'Cochlodinium', 'Dinophysis_spp', 'Gymnodinium_spp', 'Lingulodinium_polyedra', 'Prorocentrum_spp','Pseudo_nitzschia_delicatissima_group','Pseudo_nitzschia_seriata_group','pDA', 'Ammonium','Avg_Chloro','Avg_Phaeo','Nitrate','Phosphate', 'Silicate', 'Temp')
         
#Add a column for units - need this for Shiny app 
HABMAP_Data_Long_Units = HABMAP_Data_Long %>% 
  mutate(Units = ifelse(grepl("pDA", Observations),'ng/mL',
                        ifelse(grepl('Temp', Observations), "Celsius",
                               ifelse(grepl("'Avg_Chloro'|'Avg_Phaeo'", Observations), "mg/m3",
                                      ifelse(grepl("
                                      'Akashiwo_sanguinea'|
                                      'Alexandrium_spp'|
                                      'Ceratium'|
                                      'Cochlodinium'|
                                      'Dinophysis_spp'|
                                      'Gymnodinium_spp'|
                                      'Lingulodinium_polyedra'|
                                      'Prorocentrum_spp'|
                                      'Pseudo_nitzschia_delicatissima_group'|
                                      'Pseudo_nitzschia_seriata_group'", Observations), "cells/L", "uM")))))

HABMAP_Data_Long_Units2 = HABMAP_Data_Long_Units %>%
  mutate(Date = as.Date(time)) %>%
  select(Location_Code, Date, Observations, Measurement, Units) %>%
  as.tibble()

#Replace all NaN with NA
#test_NaN = HABMAP_Data_Long_Units2 %>% summarise(count=sum(is.nan(Measurement))) #R is not recgonizing NaN 

#test_NA = HABMAP_Data_Long_Units2 %>% summarise(count=sum(is.na(Measurement))) #R is not recgonizing NA

#HABMAP_Data_Long_Units2$Measurement[is.nan(HABMAP_Data_Long_Units2$Measurement)] = NA #doesnt work since R is not recgonizing NaN

HABMAP_Data_Long_Remove_NaN = HABMAP_Data_Long_Units2 %>%
  mutate(Measurement = replace(Measurement, Measurement == "NaN", NA)) %>% #55,548X5
  mutate(Measurement = as.integer(Measurement))

test_NA = HABMAP_Data_Long_Remove_NaN %>% #12779 NAs
  summarise(count=sum(is.na(Measurement))) 

test_NaN = HABMAP_Data_Long_Remove_NaN %>% #0 NaN
  summarise(count=sum(is.nan(Measurement))) 

#Save HABMAP long formated data table 
write_rds(HABMAP_Data_Long_Remove_NaN, "California_HAB/HABMAP_Data_Long_Units.rds")

```
